%-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}

\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}

\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

\definecolor{MidnightBlue}{HTML}{0f63ac} % Define the color MidnightBlue

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{\textcolor{MidnightBlue}}{0em}{\textcolor{MidnightBlue}}[\color{MidnightBlue}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}



\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

\newcommand{\customfooter}[2]{  % Add second parameter for second line of the footer
  \fancyfoot[L]{\footnotesize \color{black}{#1}}     % Left-aligned custom text
  \fancyfoot[R]{\footnotesize \color{black}{Page \thepage}} % Right-aligned page number
  \renewcommand{\footrulewidth}{0.4pt} % Footrule thickness
  \fancyheadoffset[L,R]{5pt} % Ensure the rule extends to page edges
  \renewcommand{\footrule}{\color{MidnightBlue}\hrule width \textwidth height \footrulewidth} % Full-width footrule in MidnightBlue
}

%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%

\newcommand{\name}{Zahra Helalizadeh} % Your Name
\newcommand{\phone}{9901238242} % Your Phone Number
\newcommand{\emaila}{zahra.helalizadeh.eesut@gmail.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont

%----------HEADING-----------------
\textcolor{MidnightBlue}{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} & 
  \raisebox{0.0\height}{\footnotesize \faPhone}\ +98-\phone\\
  Electrical Engineering Bachelor's Student & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}}\ \emaila \\
  Major in Digital Systems & \href{https://github.com/zarahlz}{\raisebox{0.0\height}{\footnotesize \faGithub}}\ GitHub Profile \\
  Sharif University of Technology & \href{https://www.linkedin.com/in/zahra-helalizadeh}{\raisebox{0.0\height}{\footnotesize \faLinkedin}}\ LinkedIn Profile
\end{tabularx}
}

\vspace{-5mm}

%-----------INTERESTS-----------------

\section{{\textbf{Research Interests}}}

  \vspace{-0.5mm}

    \resumeSubHeadingListStart
        \begin{multicols}{2}
            \resumeItem{Data Structures \& Algorithms}{}
            \vspace{-3.5mm}
            \resumeItem{Microprocesso Design \& Architecture}{}
            \vspace{-3.5mm}
            \resumeItem{FPGA \& VLSI Circuit Design}{}
            \vspace{-3.5mm}
            \resumeItem{Dara Science}{}
            \vspace{-3.5mm}
            \resumeItem{Machine Learning}{}
            \vspace{-3.5mm}
            \resumeItem{IoT Systems}{}
        \end{multicols}
    \resumeSubHeadingListEnd

\vspace{-10.5mm}


%-----------EDUCATION-----------
\section{\textcolor{MidnightBlue}{\textbf{Education}}}

  \vspace{-0.5mm}

  \resumeSubHeadingListStart
    \resumeSubheading
      {Sharif University of Technology}{Cumulative Average: 16.32/20}
      {Bachelor’s Degree in Electrical Engineering, Major in Digital Systems}{2021 - Present}
      
      \vspace{-1.5mm}

      \resumeSubheading
      {Farzanegan's School of Development of Exceptional Talents}{Cumulative Average: 19.45/20}
      {Post Graduate Diploma in Mathematics and Physics}{2018 -- 2021}
  \resumeSubHeadingListEnd

\vspace{-8.5mm}


%-----------RESEARCH EXPERIENCE-----------------
\section{{\textbf{Research Experience}}}
  \resumeSubHeadingListStart

    \vspace{-0.5mm}

    \resumeSubheading
      {Hardware Optimization for Large Language Models}{\textit{Fall 2024 - Present}}
      {Hardware Optimizer}{\textcolor{MidnightBlue}{\href{https://scholar.google.com/citations?user=8HsoXAUAAAAJ&hl=en}{Prof. B. Khalaj}}}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Developing techniques for hardware optimization in large language models.}
        \item {Focusing on efficient parameter storage and dynamic memory management.}
        \item {Enabling execution of models larger than available memory.}
        \item {Enhancing inference speed and resource utilization on constrained systems.}
      \resumeItemListEnd
    
    \vspace{-4.5mm}

    \resumeSubheading
      {Design \& Implementation of Field Programmable Gate Arrays}{\textit{Summer 2024 - Present}}
      {Hardware Designer}{\textcolor{MidnightBlue}{\href{https://scholar.google.com/citations?user=PkLFUfkAAAAJ&hl=en}{Prof. A. Fotowat}}}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Designing FPGA layouts focusing on configurable logic blocks and connection blocks.}
        \item {Optimizing routing efficiency and resource utilization in line with technical specifications.}
        \item {Exploring innovative digital design techniques for power efficiency.}
        \item {Implementing dynamic reconfiguration strategies to enhance FPGA architecture.}
      \resumeItemListEnd

      \vspace{-4.5mm}

      \resumeSubheading
      {Real-Time IoT Video Streaming System}{\textit{Summer 2024 - Present}}
      {Linux Developer}{\textcolor{MidnightBlue}{\href{https://scholar.google.com/citations?user=8HsoXAUAAAAJ&hl=en}{Prof. B. Khalaj}}}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Developed a video streaming system for security cameras using FFmpeg, GStreamer, and OpenCV.}
        \item {Implemented face recognition algorithms for real-time detection and identification.}
        \item {Built an RTSP framework to capture and stream low-latency video feeds.}
        \item {Conducted performance testing to ensure reliability and efficiency in IoT settings.}
      \resumeItemListEnd    
    
  \resumeSubHeadingListEnd
\vspace{-12mm}

%-----------COURSE PROJECTS-----------------
\section{{\textbf{Related Coursework}}}
  \resumeSubHeadingListStart

    \vspace{-0.5mm}

    \resumeSubheading
      {Parallel Algorithm Design \& Programming}{\textit{Spring 2024}}
      {CUDA Developer}{\textcolor{MidnightBlue}{\href{https://scholar.google.com/citations?user=kCBJNHwAAAAJ&hl=en}{Prof. M. Hashemi}}}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Designed and implemented parallel algorithms using CUDA for high-performance computing.}
        \item {Optimized computational efficiency for data-intensive tasks.}
        \item {Developed scalable solutions within the framework of parallel architecture.}
      \resumeItemListEnd

    \vspace{-4.5mm}
    
    \resumeSubheading
      {Signal Processing on FPGA Systems}{\textit{Spring 2024}}
      {Digital Signal Processing Contributor}{\textcolor{MidnightBlue}{\href{https://scholar.google.ca/citations?user=lWSKYd4AAAAJ&hl=en}{Prof. M. Shabany}}}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Designed an FPGA/ASIC system for signal generation and processing on a Zynq platform.}
        \item {Gained expertise in digital communication protocols and signal processing techniques.}
        \item {Enhanced understanding of FPGA implementation in signal applications.}
      \resumeItemListEnd
    
    \vspace{-4.5mm}
    
    \resumeSubheading
      {Performance Optimization Algorithms \& Programming}{\textit{Spring 2024}}
      {Microprocessor Systems Contributor}{\textcolor{MidnightBlue}{\href{https://www.researchgate.net/profile/Mohammad-Movahedin}{Prof. M. Movahedin}}}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Optimized matrix multiplication in C using advanced techniques.}
        \item {Employed pointer manipulation and cache optimization for enhanced performance.}
        \item {Utilized parallel processing with OpenMP to increase computational speed.}
      \resumeItemListEnd

    \vspace{-4.5mm}
    
    \resumeSubheading
      {Digital Signal Analysis}{\textit{Spring 2023}}
      {Data Analyst}{\textcolor{MidnightBlue}{\href{https://scholar.google.com/citations?user=bLuKrjgAAAAJ&hl=en}{Prof. H. Aghajan}}}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Conducted EEG signal analysis using advanced MATLAB techniques.}
        \item {Extracted insights to understand brain activity and identify unique brainwave patterns.}
        \item {Aided in the interpretation of complex neurological data.}
      \resumeItemListEnd
    
    \vspace{-4.5mm}
    
    \resumeSubheading
      {Web Development \& Application Programming}{\textit{Spring 2022}}
      {Full-Stack Developer}{\textcolor{MidnightBlue}{\href{https://scholar.google.com/citations?user=8hv_HpKBHhoC&hl=en}{Prof. B. Vahdat}}}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Developed full-stack web applications with responsive interfaces using HTML and CSS.}
        \item {Built a Java-based messaging application with SQL integration for efficient data management.}
        \item {Enhanced user communication through effective back-end design.}
      \resumeItemListEnd

    \vspace{-4.5mm}

    \customfooter{}{}
    \clearpage

  \resumeSubHeadingListEnd
\vspace{-10mm}

%-----------COURSE PROJECTS-----------------
\section{{\textbf{Related Coursework (Continued)}}}
  \resumeSubHeadingListStart

    \vspace{-0.5mm}
    
    \resumeSubheading
      {Game Development \& Graphical Programming}{\textit{Fall 2021}}
      {C++ and SDL Developer}{\textcolor{MidnightBlue}{\href{https://scholar.google.com/citations?user=8hv_HpKBHhoC&hl=en}{Prof. B. Vahdat}}}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Mastered game development in C++ using SDL for multimedia handling.}
        \item {Created interactive gaming experiences by integrating audiovisual components.}
        \item {Demonstrated proficiency with OpenGL and Direct3D for graphical rendering.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-12mm}

%-----------EXPERIENCE-----------------
\section{{\textbf{Technical Experience}}}
  \resumeSubHeadingListStart

    \vspace{-0.5mm}

    \resumeSubheading
      {Web Development \& Front-End Programming}{\textit{Fall 2023}}
      {Front-End Developer}{\textcolor{MidnightBlue}{\href{http://react-sut.com/}{ReACT 2024}}}
      \vspace{-2.0mm}
      \resumeItemListStart
        \item {Developed a dynamic website for ReACT 2024 using Django and JavaScript.}
        \item {Implemented features to enhance user engagement.}
        \item {Contributed to the success of a conference with 500+ participants.}
        \item {Collaborated with teams for seamless design integration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\vspace{-12mm}


%-----------Relevant Courses-----------------
\section{{\textbf{Relevant Courses}}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
    \resumeSubheading{Data Analytics \& Intelligent Systems}{} 
    {}{} 
    \vspace{-6.0mm}
    \resumeItemListStart
        \item {Machine Learning: N \hfill \textit{Fall 2024}}
        \item {Artificial Intelligence: N \hfill \textit{Fall 2024}}
        \item {Dara Science: A \hfill \textit{Fall 2024}}
        \item {Large Language Model: A \hfill \textit{Summer 2024}}
    \resumeItemListEnd

\vspace{-4.0mm}

    \resumeSubheading{Digital Systems \& Hardware Design}{} 
    {}{} 
    \vspace{-6.0mm}
    \resumeItemListStart
        \item {VLSI Design$^{\dagger}$: N \hfill \textit{Fall 2024}}
        \item {Computer Interface Circuits$^{\dagger}$: N \hfill \textit{Fall 2024}}
        \item {Microprocessor Systems Lab: N \hfill \textit{Spring 2024}}
        \item {ASIC/FPGA Systems Lab: 19.1/20 \hfill \textit{Spring 2024}}
        \item {ASIC/FPGA System Design: 15.8/20 \hfill \textit{Spring 2024}}
        \item {Microprocessor Systems Design: 17/20 \hfill \textit{Spring 2024}}
        \item {Computer Architecture \& Microprocessors \& Lab: 17.2/20 \hfill \textit{Spring 2023}}
        \item {Logical Circuits \& Digital Systems \& Lab: 16.5/20 \hfill \textit{Fall 2022}}
    \resumeItemListEnd

\vspace{-4.0mm}

    \resumeSubheading{Algorithms \& Programming}{} 
    {}{} 
    \vspace{-6.0mm}
    \resumeItemListStart
        \item {Parallel Programming \& Architecture$^{\dagger}$: 16.2/20 \hfill \textit{Spring 2024}}
        \item {Data Structures \& Algorithms: 18.5/20 \hfill \textit{Spring 2024}}
        \item {Object Oriented Programming: 20/20 \hfill \textit{Spring 2022}}
        \item {Fundamentals of Programming: 19.6/20 \hfill \textit{Fall 2021}}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-11.5mm}

%-----------Positions of Responsibility-----------------
\section{{\textbf{Teaching Experience}}}
  \resumeSubHeadingListStart

    \resumeSubheading{Computer Architecture \& Microprocessor Course}{} 
    {Teaching Assistant}{Fall 2023 - Present} 
    \vspace{-2.0mm}
    \resumeItemListStart
      \item {Graded assignments, midterms, and finals, assisted in laboratory sessions. \hfill \footnotesize \textcolor{MidnightBlue}{\textit{\href{https://scholar.google.de/citations?user=nR98aV4AAAAJ&hl=en}{Prof. S. Bagheri}}}}
      \item {Designed and graded assignments, graded lab assignments. \hfill \footnotesize \textcolor{MidnightBlue}{\textit{\href{https://scholar.google.com/citations?user=gJkJ9wUAAAAJ&hl=en}{Prof. E. Cheshmikhani}}}}
      \item {Graded quizzes, assisted students with problem-solving. \hfill \footnotesize \textcolor{MidnightBlue}{\textit{\href{https://www.researchgate.net/profile/Mohammad-Movahedin}{Prof. M. Movahedin}}}}
    \resumeItemListEnd

    \vspace{-4.0mm}
    
    \resumeSubheading{Logical Circuits \& Digital Systems Course}{} 
    {Teaching Assistant}{Fall 2023 - Present} 
    \vspace{-2.0mm}
    \resumeItemListStart
      \item {Designed and graded homework assignments and quizzes. \hfill \footnotesize \textcolor{MidnightBlue}{\textit{\href{http://link_to_prof_movahedin.com}{Prof. M. Movahedin}}}}
      \item {Assisted in laboratory and graded lab assignments. \hfill \footnotesize \textcolor{MidnightBlue}{\textit{\href{https://www.researchgate.net/profile/Mahmoud-Tabandeh}{Prof. M. Tabandeh}}}}
    \resumeItemListEnd

    \vspace{-4.0mm}

    \resumeSubheading{Basic Programming Course}{} 
    {Teaching Assistant}{Fall 2024 - Present} 
    \vspace{-2.0mm}
    \resumeItemListStart
      \item {Designed and graded quizzes and exams. \hfill \footnotesize \textcolor{MidnightBlue}{\textit{\href{https://scholar.google.com/citations?user=FWnadoAAAAAJ&hl=en}{Prof. A. Abrishami}}}}
    \resumeItemListEnd

    \vspace{-4.0mm}

  \resumeSubHeadingListEnd

\vspace{-7.5mm}


%-----------SKILLS-----------------
\section{{\textbf{Skills}}}

  \resumeSubHeadingListStart
    \resumePOR{Programming Languages: }{C/C++, CUDA, Java, Python, MATLAB}{}
    \vspace{-1.0mm}
  \resumeSubHeadingListEnd

  \vspace{-7.0mm}

  \resumeSubHeadingListStart
    \resumePOR{Web Development: }{HTML, CSS, JavaScript, Django}{}
    \vspace{-1.0mm}
  \resumeSubHeadingListEnd

  \vspace{-7.0mm}

  \resumeSubHeadingListStart
    \resumePOR{Database Management: }{mySQL, PostgreSQL}{}
    \vspace{-1.0mm}
  \resumeSubHeadingListEnd

  \vspace{-7.0mm}

  \resumeSubHeadingListStart
    \resumePOR{Hardware Description Languages: }{VHDL, Verilog}{}
    \vspace{-1.0mm}
  \resumeSubHeadingListEnd

  \vspace{-7.0mm}

  \resumeSubHeadingListStart
    \resumePOR{Operating Systems: }{Windows, Linux}{}
    \vspace{-1.0mm}
  \resumeSubHeadingListEnd

  \vspace{-7.0mm}

  \resumeSubHeadingListStart
    \resumePOR{Technical Skills: }{Microsoft Office, LaTeX}{}
    \vspace{-1.0mm}
  \resumeSubHeadingListEnd

  \vspace{-7.0mm}

  \resumeSubHeadingListStart
    \resumePOR{Languages: }{Advanced English, Native Persian}{}
    \vspace{-1.0mm}
  \resumeSubHeadingListEnd
  
\customfooter{$\dagger$: Graduate Course \hspace{10mm} N: Not available \hspace{10mm} A: Audited}

\clearpage

%-------------------------------------------
\end{document}
